## MDSC - 202(P)

## Final Lab Test

**Author: Akula Venkata Satya Sai Gopinadh**

**Regd NO: 22228**

## **DATASET: 3.csv**

```{r}
print(getwd())
```

```{r}
setwd("C:/Users/Msc 1/Desktop/MDSC-202")
print(getwd())
```

```{r}
data <- read.csv("3.csv")
print(data)
```

```{r}
print(ncol(data))
```

```{r}
print(nrow(data))
```

### QQ plot is used for checking the outliers.

```{r}
# For Column name CITCRP
qqnorm(data$CITCRP)
qqline(data$CITCRP)
```

### For the above column we can see that the outliers are very less. We can see only two outliers are there in the above  QQ plot for the first column.

```{r}
# For Column name CONED - column 2
qqnorm(data$CONED)
qqline(data$CONED)
```

### For the above column we can see that the outliers are little more. We outliers are there in the above  QQ plot for the second column.

```{r}
# For Column name CONTIL - column 3
qqnorm(data$CONTIL)
qqline(data$CONTIL)

```

### For the above column we can see that the outliers are little more. We outliers are there in the above  QQ plot for the third column.

```{r}
# For Column name DATGEN - column 4
qqnorm(data$DATGEN)
qqline(data$DATGEN)
```

### For the above column we can see that the outliers are little more. We outliers are there in the above  QQ plot for the fourth column.

```{r}
# For Column name DELTA - column 5
qqnorm(data$DELTA)
qqline(data$DELTA)
```

### For the above column we can see that the outliers are little more. We outliers are there in the above  QQ plot for the fifth column.

```{r}
# For Column name RKFREE - column 6
qqnorm(data$RKFREE)
qqline(data$RKFREE)

```

### For the above column we can see that the outliers are little less compared with other columns. We outliers are there in the above  QQ plot for the second column.

```{r}

```

```{r}

```

```{r}

```
